A Comparision of Bootstrap Methods

### 2022-12-02 project/PaperTemplate/paper.Rmd
added parallel to speed things up

keywords:
- 3 to 6 keywords
- that do not appear in the title

@@

```{r setup, include = FALSE}
library(tidyverse)
library(mosaic)
library(mdsr)
library(knitr)
library(kableExtra)
library(boot)
```

# Introduction
To be added later

@@

```{r}

orig_mean <- mean(~ Dec, data = SnowGR) # theta hat

@@

for (i in 1:nboot) {
  resampled <- as.data.frame(mosaic::resample(SnowGR, replace = TRUE))
  mean[i] <- mean(~Dec, data = resampled)
  sd[i] <- sd(~Dec, data = resampled)
 # se[i] <- sd[i]/nrow(resampled)
#  t_stat[i] <- (mean[i] - orig_mean)/se[i]
}

dec_means <- as.data.frame(mean)
#dec_t_stat <- as.data.frame(t_stat)

```{r}

#set.seed(495)
#dec_means <- do(10000)*mean(~ Dec, data = mosaic::resample(SnowGR, replace = TRUE))

gf_dhistogram(~ mean, data = dec_means) %>%
  gf_dens() %>%
  gf_labs(title = "Histogram of 10,000 Bootstrapped Mean Dec Values")
```

@@

  for (i in 1:simulation_reps){
    #X <- rnorm(n, trueparameter, 3)
    X <- rgamma(n, shape = 1, scale = 4)
    values <- data.frame(X)
    output <- findCIs(values, 2000)
    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & trueparameter <= output$`Standard Interval`[2]
    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & trueparameter <= output$`Percentile Interval`[2]
    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] & trueparameter <= output$`BC Interval`[2]
    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & trueparameter <= output$`BCa Interval`[2]
    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & trueparameter <= output$`Studentized Interval`[2]

  }

@@

```{r}
#10 100 500 1000
data2 <- matrix(nrow = 3, ncol = 6)

for (i in 1:3) {
  output2 <- run_simulation_gamma(10, 10^i)
  data2[i, 1] <- 10^i
  data2[i, 2] <- output2[1]
  data2[i, 3] <- output2[2]
  data2[i, 4] <- output2[3]
  data2[i, 5] <- output2[4]
  data2[i, 6] <- output2[5]
}

output3 <- as.data.frame(data2) %>% 
  rename("sample_size" = V1, "standard" = V2, "percentile" = V3, "BC" = V4, "BCa" = V5, "studentized" = V6)

output4 <- output3 %>%
  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

ggplot(data = output4, aes(x = sample_size, y = prop, color = method))+
  geom_point() +
  geom_line()

@@

```{r}

Y <- rgamma(5, shape = 8, scale = 2)
Y

@@

>>>>

keywords:
- confidence interval
- simulation
- percentile
- bias-corrected
- acceleration
- studentized

@@

```{r setup, include = FALSE}
library(tidyverse)
library(mosaic)
library(mdsr)
library(knitr)
library(kableExtra)
library(boot)
library(gridExtra)
```

# Introduction
Bootstrapping is an important tool in Statistics, even more so, now that there is access to a higher-level of computing power. We use bootstrapping to find an estimate of a desired population parameter from a given sample, without making any assumptions about any underlying distributions of the sample.

@@

```{r}
orig_mean <- mean(~ Dec, data = SnowGR) # theta hat

@@

for (i in 1:nboot) {
  resampled <- as.data.frame(mosaic::resample(SnowGR, replace = TRUE))
  mean[i] <- mean(~Dec, data = resampled)
  sd[i] <- sd(~Dec, data = resampled)
}

dec_means <- as.data.frame(mean)
```

```{r}
gf_dhistogram(~ mean, data = dec_means) %>%
  gf_dens() %>%
  gf_labs(title = "Histogram of 10,000 Bootstrapped Mean Dec Values")
```

@@

  for (i in 1:simulation_reps){
    X <- rgamma(n, shape = 1, scale = 4)
    values <- data.frame(X)
    output <- findCIs(values, 2000)
    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
      trueparameter <= output$`Standard Interval`[2]
    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
      trueparameter <= output$`Percentile Interval`[2]
    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
      trueparameter <= output$`BC Interval`[2]
    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
      trueparameter <= output$`BCa Interval`[2]
    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
      trueparameter <= output$`Studentized Interval`[2]
  }

@@

```{r}
run_simulation_log_normal <- function(num_reps, sample_size){
  set.seed(495)
  simulation_reps <- num_reps
  trueparameter <- exp(1/2)
  n <- sample_size

  for (i in 1:simulation_reps){
    X <- rlnorm(n, meanlog = 0, sdlog = 1)
    values <- data.frame(X)
    output <- findCIs(values, 2000)
    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
      trueparameter <= output$`Standard Interval`[2]
    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
      trueparameter <= output$`Percentile Interval`[2]
    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
      trueparameter <= output$`BC Interval`[2]
    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
      trueparameter <= output$`BCa Interval`[2]
    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
      trueparameter <= output$`Studentized Interval`[2]
  }
  ci_prop <- colSums(ci)/simulation_reps
  ci_prop
}

@@

```{r}
run_simulation_normal <- function(num_reps, sample_size){
  set.seed(495)
  simulation_reps <- num_reps
  trueparameter <- 0
  n <- sample_size

  for (i in 1:simulation_reps){
    X <- rnorm(n, mean = 0, sd = 1)
    values <- data.frame(X)
    output <- findCIs(values, 2000)
    ci[i, 1] <- trueparameter >= output$`Standard Interval`[1] & 
      trueparameter <= output$`Standard Interval`[2]
    ci[i, 2] <- trueparameter >= output$`Percentile Interval`[1] & 
      trueparameter <= output$`Percentile Interval`[2]
    ci[i, 3] <- trueparameter >= output$`BC Interval`[1] &
      trueparameter <= output$`BC Interval`[2]
    ci[i, 4] <- trueparameter >= output$`BCa Interval`[1] & 
      trueparameter <= output$`BCa Interval`[2]
    ci[i, 5] <- trueparameter >= output$`Studentized Interval`[1] & 
      trueparameter <= output$`Studentized Interval`[2]
  }
  ci_prop <- colSums(ci)/simulation_reps
  ci_prop
}

```{r}
collect_data_gamma <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  simulation_reps <- sim_reps
  sample_sizes <- c(10, 25, 50, 100, 250)

  for (i in 1:5) {
    output2 <- run_simulation_gamma(simulation_reps, sample_sizes[i])
    data2[i, 1] <- sample_sizes[i]
    data2[i, 2:6] <- output2
  }

  gamma_output <- as.data.frame(data2) %>% 
    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
  gamma_output
}

```{r}
collect_data_log_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  simulation_reps <- sim_reps
  sample_sizes <- c(10, 25, 50, 100, 250)

  for (i in 1:5) {
    output2 <- run_simulation_log_normal(simulation_reps, sample_sizes[i])
    data2[i, 1] <- sample_sizes[i]
    data2[i, 2:6] <- output2
  }

  normal_output <- as.data.frame(data2) %>% 
    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
  normal_output
}

```{r}
collect_data_normal <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  simulation_reps <- sim_reps
  sample_sizes <- c(10, 25, 50, 100, 250)

  for (i in 1:5) {
    output2 <- run_simulation_normal(simulation_reps, sample_sizes[i])
    data2[i, 1] <- sample_sizes[i]
    data2[i, 2:6] <- output2
  }

  normal_output <- as.data.frame(data2) %>% 
    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
  normal_output
}

```{r, cache = TRUE}
set.seed(495)
gamma_data <- collect_data_gamma(30)
normal_data <- collect_data_normal(30)
log_normal_data <- collect_data_log_normal(30)
```

```{r}
  gamma_data1 <- gamma_data %>%
    pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

  gamma_fig <- ggplot(data = gamma_data1, aes(x = Sample_Size, y = prop, color = method))+
    geom_point() +
    geom_line() + 
    labs(title = "Proportion of CIs that Contain the True Parameter from Gamma Distibution",
         x = "Sample Size", y = "Proportion (of xyz Simulations)", color = "Method") +
    theme_light()

  gamma_table <- gamma_data %>%
    kable(booktabs = TRUE, align = "c", caption = "gamma", col.names = gsub("[_]", " ", names(gamma_data)))

  gamma_table
  gamma_fig

@@

```{r}
library(parallel)
numCores <- detectCores()
#simulation_reps <- 30
#simulation_rep <- seq(1,simulation_reps)
#sample_size <- 20
#  simulation_reps <- num_reps

run_simulation_normal1 <- function(simulation_rep){
  trueparameter <- 0

  X <- rnorm(sample_sizes, mean = 0, sd = 1)
  values <- data.frame(X)
  output <- findCIs(values, 2000)
  ci <- matrix(c(trueparameter >= output$`Standard Interval`[1] & 
    trueparameter <= output$`Standard Interval`[2],
    trueparameter >= output$`Percentile Interval`[1] & 
    trueparameter <= output$`Percentile Interval`[2],
    trueparameter >= output$`BC Interval`[1] &
    trueparameter <= output$`BC Interval`[2],
    trueparameter >= output$`BCa Interval`[1] & 
    trueparameter <= output$`BCa Interval`[2],
    trueparameter >= output$`Studentized Interval`[1] & 
    trueparameter <= output$`Studentized Interval`[2]), nrow = 1)
  res <- rbind(data.frame(), ci)
  res
}

  collect_data_normal1 <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)

  sample_sizes = 10

  for (i in 1:5) {
    #output2 <- run_simulation_normal1(simulation_reps)
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_normal1, mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- colSums(df)/sim_reps

    data2[i, 1] <- sample_sizes
    data2[i, 2:6] <- ci_prop
    sample_sizes <- sample_sizes*2
  }

  normal_output <- as.data.frame(data2) %>% 
    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
  normal_output
  }

    xyzw <- collect_data_normal1(20)
